Reopt

### 2023-04-26 src/reopt_api.Rmd
trying to read in utility data

```{r}
# create list of default inputs for each city
inputs <- list(
  ModuleType = "Premium",
  DCACratio = 1.35,
  System_losses = 5,
  FederalIncentive = 30
)
```

@@

# Set the payload for the job submission request
payload <- list(
  "Scenario" = list(
    "Site" = list(
      "longitude" = -118.1164613,
      "latitude" = 34.5794343,
      "roof_squarefeet" = 5000.0,
      "land_acres" = 1.0,
      "PV" = list(
        "installed_cost_us_dollars_per_kw" = 2000.0,
        "tilt" = 34.579,
        "degradation_pct" = 0.005,
        "macrs_option_years" = 5,
        "federal_itc_pct" = 0.3,
        "module_type" = 0,
        "array_type" = 1,
        "om_cost_us_dollars_per_kw" = 16.0,
        "macrs_itc_reduction" = 0.5,
        "azimuth" = 180.0,
        "federal_rebate_us_dollars_per_kw" = 350.0
      ),
      "LoadProfile" = list(
        "doe_reference_name" = "MidriseApartment",
        "annual_kwh" = 10000000.0,
        "city" = "LosAngeles"
      ),
      "Storage" = list(
        "total_rebate_per_kw" = 100.0,
        "macrs_option_years" = 5,
        "can_grid_charge" = TRUE,
        "macrs_bonus_pct" = 0.4,
        "macrs_itc_reduction" = 0.5,
        "total_itc_pct" = 0,
        "installed_cost_us_dollars_per_kw" = 1000.0,
        "installed_cost_us_dollars_per_kwh" = 500.0,
        "replace_cost_us_dollars_per_kw" = 460.0,
        "replace_cost_us_dollars_per_kwh" = 230.0
      ),
      "ElectricTariff" = list(
        "urdb_label" = "5ed6c1a15457a3367add15ae"
      ),
      "Financial" = list(
        "escalation_pct" = 0.026,
        "offtaker_discount_pct" = 0.081,
        "owner_discount_pct" = 0.081,
        "analysis_years" = 20,
        "offtaker_tax_pct" = 0.4,
        "owner_tax_pct" = 0.4,
        "om_cost_escalation_pct" = 0.025
      )
    )
  )
)

@@

```{r}
results_url <- paste0("https://developer.nrel.gov/api/reopt/stable/job/", run_uuid, "/results")

@@

## energy goals
#cost_savings and clean_energy
## inputs not default 
host_eff <- 0
scc = 185

>>>>

```{r}
# create list of default inputs for each city
inputs <- list(
  offtaker_tax_pct = 0, # host effective tax rate
  co2_cost_us_dollars_per_tonne = 185,
  module_type = 1,
  dc_ac_ratio = 1.35,
  losses = 0.05,
  federal_itc_pct = 0.3,
  location = "roof", # restrict projects to roof
  can_net_meter = TRUE

)
```

```{r}
# Set the payload for the job submission request
payload <- list(
  "Scenario" = list(
    "Site" = list(
      "longitude" = -118.1164613,
      "latitude" = 34.5794343,
      "roof_squarefeet" = 5000.0,
      "land_acres" = 1.0,
      "PV" = list(
        "installed_cost_us_dollars_per_kw" = 2000.0,
        "federal_rebate_us_dollars_per_kw" = 350.0,
        # changes from default
        "module_type" = 1,
        "dc_ac_ratio" = 1.35,
        "losses" = 0.05,
        "federal_itc_pct" = 0.3,
        "location" = "roof", # restrict projects to roof
        "can_net_meter" = TRUE
      ),
      "LoadProfile" = list(
        "doe_reference_name" = "MidriseApartment",
        "annual_kwh" = 10000000.0,
        "city" = "LosAngeles"
      ),
      "ElectricTariff" = list(
        "urdb_label" = "5ed6c1a15457a3367add15ae",
        "add_tou_energy_rates_to_urdb_rate" = TRUE
      ),
      "Financial" = list(
        "escalation_pct" = 0.026,
        "offtaker_discount_pct" = 0.081,
        "owner_discount_pct" = 0.081,
        "analysis_years" = 20,
        "offtaker_tax_pct" = 0.4,
        "owner_tax_pct" = 0.4,
        "om_cost_escalation_pct" = 0.025
      )
    )
  )
)

```{r}
## open EI api
openEI_api_key <- "rU6MEqhK9OJ7obAnmcbzYhpFOenfBM5Q8GF0yJFA"

openEI_start <- "https://api.openei.org/utility_rates?version=latest&format=json&sector=Residential&detail=full&approved=true&address=26900&"
# Set the URL for the job submission endpoint

openEI_url <- paste0(openEI_start, "api_key=", openEI_api_key)

EIresponse <- GET(openEI_url)
content <- content(EIresponse, "text")
json <- fromJSON(content)

EIoutput_df <- data.frame(
  label = json$items$label,
  utility = json$items$utility,
  approved = json$items$approved,
  rate_name = json$items$name)

  # extract utility rate information
rates <- json$items$rate
  # print utility rate information for the city
  cat(city, "utility rates:\n")
  for (rate in rates) {
    cat("  - Name:", rate$name, "\n")
    cat("    Description:", rate$description, "\n")
    cat("    Value:", rate$value, "\n")

if (http_type(response)$status_code == 200) {
  data <- fromJSON(content(EIresponse, "text"), simplifyDataFrame = TRUE)

  # Extract relevant information from the data
  utility_name <- data$items[[1]]$utility_name
  utility_type <- data$items[[1]]$sector
  rate_name <- data$items[[1]]$name
  start_date <- data$items[[1]]$start_date
  end_date <- data$items[[1]]$end_date
  rate_structure <- data$items[[1]]$rate_structure
  energy_rate <- data$items[[1]]$rate
  demand_rate <- data$items[[1]]$demand_rate

  # Print the results
  cat(sprintf("Utility name: %s\n", utility_name))
  cat(sprintf("Utility type: %s\n", utility_type))
  cat(sprintf("Rate name: %s\n", rate_name))
  cat(sprintf("Start date: %s\n", start_date))
  cat(sprintf("End date: %s\n", end_date))
  cat(sprintf("Rate structure: %s\n", rate_structure))
  cat(sprintf("Energy rate: %s\n", energy_rate))
  cat(sprintf("Demand rate: %s\n", demand_rate))
} else {
  cat(sprintf("Failed to retrieve data (status code %s)", http_type(response)$status_code))
}

@@

# list of cities
cities <- c("San Francisco", "Los Angeles", "New York")

# loop through each city and get utility rate information
for (city in cities) {
  # construct URL with city name as parameter
  url <- paste0("https://api.openei.org/utility_rates?version=3&format=json&address=", gsub(" ", "+", city))
  # make API call
  response <- GET(url)
  # extract content and parse as JSON
  content <- content(response, "text")
  json <- fromJSON(content)
  # extract utility rate information
  rates <- json$items$rate
  # print utility rate information for the city
  cat(city, "utility rates:\n")
  for (rate in rates) {
    cat("  - Name:", rate$name, "\n")
    cat("    Description:", rate$description, "\n")
    cat("    Value:", rate$value, "\n")
  }
}
```

```{r STUFF TO WORK ON}

net_metering_limit_kw # by state

@@

```{r}
## GET RESULTS FROM REOPT
results_url <- paste0("https://developer.nrel.gov/api/reopt/stable/job/", run_uuid, "/results")

@@
